\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage{tabularx}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage{hyperref}
    \usepackage{navigator}

% Ensure that generate pdf is machine readable/ATS parsable:
\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[T1]{fontenc}
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\vspace*{-40pt}

%==== Summary ====%
\vspace*{-10pt}
\outline{1}[Title]{}
\begin{center}
	{\Huge \scshape {Payas P Relekar}}\\
	\href{mailto:relekarpayas@gmail.com}{relekarpayas@gmail.com} $\cdot$ \href{mailto:payas@relekar.org}{payas@relekar.org} \\
	\href{tel:+91-8459867068}{+91-8459867068} $\cdot$ \href{https://git.bhankas.org/payas/}{Forgejo} $\cdot$ \href{https://github.com/bhankas/}{GitHub}\\
\end{center}

\outline{1}[Summary]{Summary}
\header{Summary}
\vspace{1mm}

\begin{itemize} \itemsep 1pt
	\item Payas Relekar is a Software Engineer at FPL Technologies (OneCard) in Pune, India. He is an experienced software developer with 5+ years of experience and Masters in Digital Systems from Savitribai Phule Pune University. His versatile interests and experience include multiple domains and technology stacks.
	\item Versatile experience in developing solutions for Digital Payments, Natural Language Processing, Embedded Electronics, system administration and more.
	\item Demonstrated quick adaptability working across multiple domains and platforms, development as well as research, team oriented as well as independent work capability.
\end{itemize}

%==== Skills ====%
\outline{1}[Skills]{Skills}
\header{Skills}
\vspace{1mm}
\bgroup
\setlength{\arrayrulewidth}{0.2mm}
\def\arraystretch{1.2}
\begin{tabularx}{\textwidth}{ | X | X | }
	\hline
	\textbf{Languages/Technologies} & Java, SQL, Bash, Python, Emacs, Nix, Docker  \\
	\hline
	\textbf{Platforms}              & Linux, NixOS, AWS (EC2, Lambda, Gateway)     \\
	\hline
	\textbf{Databases}              & PostgreSQL, SQLite                           \\
	\hline
	\textbf{Tools}                  & Git, Grep/Regex, Awk, Sed                    \\
	\hline
	\textbf{Libraries/Frameworks}   & jPOS, Spring (Boot), Hibernate, TestNG, JDBi \\
	\hline
\end{tabularx}
\egroup
\vspace{2mm}

%==== Experience ====%
\outline{1}[Work Experience]{Work Experience}
\header{Work Experience}
\vspace{1mm}

\outline{2}[Unified Payments Interface]{Onecard / FPL}
\textbf{FPL Technologies (\href{https://www.getonecard.app/}{Onecard})} \\
\noindent
\begin{tabularx}{\textwidth}{ l l>{\raggedleft\arraybackslash}X}
	% \begin{tabularx}{\textwidth}{ l l l r }
	Project & : \textit{\href{https://en.wikipedia.org/wiki/Unified_Payments_Interface}{Unified Payments Interface}} &                      \\
	Role    & : \textit{Senior Software Engineer (Backend)}                                                          & Feb 2023 - Till Date \\
\end{tabularx}
\textbf{} \\
\begin{itemize} \itemsep 1pt
	\item FPL Technologies is a Technology Service Provider for multiple banks, acting as a Credit Card issuer.
	\item Implemented complete backend integration for Unified Payments Interface (UPI) from scratch, including transaction processing engine and reconciliation engine.
	\item Ownership of complete UPI integration, including architecture and design, framework implementation and improvements, Java/JDK upgrades, build system improvements \& deployment pipelines.
	\item Spearheaded existing authorization engine restructure to make amenable for splitting into microservices with zero-incident production transition.
	\item Participated in hiring and onboarding of new team members in UPI and other existing projects. Mentored freshers and new team members to speed up onboarding.
	\item \textbf{Technologies}: Java (8-21), jPOS, Hibernate, PostgreSQL, AWS, Docker, Prometheus, Micrometer
\end{itemize}

\outline{2}[ACI Secure eCommerce]{ACI Worldwide, Inc}
\textbf{ACI Worldwide, Inc} \\
\noindent
\begin{tabularx}{\textwidth}{ l l>{\raggedleft\arraybackslash}X}
	% \begin{tabularx}{\textwidth}{ l l l r }
	Project & : \textit{ACI Secure eCommerce}                                       &                     \\
	Role    & : \textit{Software Engineer} (\textit{Product Development})           & Jan 2022 - Jan 2023 \\
	Role    & : \textit{Associate Software Engineer} (\textit{Product Development}) & Jul 2019 - Dec 2021 \\
\end{tabularx}
\textbf{} \\
\begin{itemize} \itemsep 1pt
	\item ACI Secure eCommerce (formerly PAY.ON Payments Gateway/Payments Orchestration Platform) offers a white-label payment structure for omni-channel transaction processing through one payment platform: eCommerce, mCommerce and mobile point-of-sale.
	\item End-to-end feature development across multiple modules and microservices, mandate implementations across multiple connectors and APIs.
	\item Provided incident resolution, platform monitoring and ensuring stability across the stack. Acquired strong understanding of development process, tooling, infrastructure and domain expertise.
	\item Ownership for customer facing whitelabel service with System administration and Service Reliability responsibilities.
	\item Agile (Scrum and Kanban) development experience in multiple teams on separate platform modules, including APIs, configuration, business logic, platform security and front-end.
	\item Received multiple accolades for customer-centricity and integrity.
	\item \textbf{Technologies}: Java, Spring/Spring Boot, Hibernate, PostgreSQL, Linux, Git, AWS (EC2), Docker
\end{itemize}

% \pagebreak

\outline{2}[Unified Payments Framework]{ACI Worldwide, Inc}
\textbf{ACI Worldwide, Inc} \\
\begin{tabularx}{\textwidth}{ l l>{\raggedleft\arraybackslash}X}
	Project & : \textit{Universal Payments Framework, Universal Online Banker } &                     \\
	Role    & : \textit{Intern} (\textit{Product Development})                  & Jan 2019 - Jun 2019 \\
\end{tabularx}
\begin{itemize} \itemsep 1pt
	\item Universal Payments Framework (UPF) provides purpose-built payments functionality to orchestrate all aspects of payments processing for any payment type, any channel, any currency and any network.
	\item Developed and maintained interfaces between various payments APIs, with differing protocols such as SOAP, REST, ISO 8583, APACS etc. Acquired understanding of payments domain and API implementations.
	\item Implemented and extended internal test framework to interface with UPF, to allow automated test execution with simple Excel test generation. Implemented automatic test-case generation to ease on-boarding QA staff.
	\item \textbf{Technologies}: Java, SOAP, REST, Subversion, Bash, Git
\end{itemize}
\vspace{1mm}

%==== Projects ====%
\outline{1}[Open Source Contributions]{Open Source Contributions}
\header{Open Source Contributions}
\vspace{1mm}

\outline{2}[NixOS/Nixpkgs]{NixOS/Nixpkgs}
{\textbf{NixOS/Nixpkgs}} \hfill Jan 2021 - Till Date \\
\textit{Nix, Bash, Python, Go, Rust} \\
\begin{itemize}
	\item \href{https://github.com/NixOS/nixpkgs/}{Nixpkgs} is a collection of 80000+ packages and one of the most active projects on GitHub. It also describes possible configuration for a complete Linux distribution using above packages.
	\item Contributions include new and ongoing maintenance of multiple packages, implemented in different languages.
\end{itemize}

\outline{2}[GNU Emacs]{GNU Emacs}
{\textbf{GNU Emacs}} \hfill Sep 2022 - Till Date \\
\textit{Emacs-Lisp, C, TexInfo} \\
\begin{itemize}
	\item \href{https://www.gnu.org/software/emacs/}{GNU Emacs} is an extensible, customizable and free/libre text editor built on top of \href{https://en.wikipedia.org/wiki/Lisp_(programming_language)}{Lisp} dialect evaluator. \\
	\item Contributions include new Elisp packages and development tooling.\\
\end{itemize}

%==== Academic projects ====%
\outline{1}[Academic Projects]{Academic Projects}
\header{Academic Projects}
\vspace{1mm}

\outline{2}[Sarcasm Detection using Machine Learning]{Sarcasm Detection using Machine Learning}
{\textbf{Sarcasm Detection using Machine Learning}} \hfill Jan 2019 - Jun-2019\\
\textit{Python, Pytorch, SpaCy, sklearn, Pandas, Numpy} \\
\vspace{1mm}

\outline{2}[Magnetic Levitation using Real-time PID]{Magnetic Levitation using Real-time PID}
{\textbf{Magnetic Levitation using Real-time PID}} \hfill Jan 2016 - Jun 2016\\
\textit{C, Arduino} \\
\vspace*{2mm}

%==== Publications ====%
\outline{1}[Publications]{Publications}
\header{Publications}
\vspace{1mm}

\outline{2}[Survey of Machine Learning for Sarcasm Detection]{Survey of Machine Learning for Sarcasm Detection}
{\textbf{\href{https://www.ijert.org/survey-of-machine-learning-for-sarcasm-detection}{Survey of Machine Learning for Sarcasm Detection}}} \hfill 2019\\
\textit{International Journal of Engineering, Research and Technology} \\
\vspace*{2mm}

\outline{2}[Magnetic Levitation using Real-Time PID]{Magnetic Levitation using Real-Time PID}
{\textbf{\href{https://ijrat.org/downloads/Conference_Proceedings/ncseee2016/ncseee-15.pdf}{Magnetic Levitation using Real-Time PID}}} \hfill 2016\\
\textit{National Conference for Students in Electrical and Electronics Engineering, VIIT} \\
\vspace*{2mm}

%==== Education ====%
\outline{1}[Education]{Education}
\header{Education}
\vspace{1mm}
\bgroup
\def\arraystretch{1.2}
% {\renewcommand{\arraystretch}{1.2}}
\begin{tabularx}{\textwidth}{ | X | c | }
	\hline

	\textbf{Master of Engineering} (Electronics) in Digital Systems       &                   \\
	Pune University                                                       & \textit{8.48}     \\
	\hline

	\textbf{Bachelor of Engineering} in Electronics \& Telecommunications &                   \\
	Pune University                                                       & \textit{62.5 \%}  \\
	\hline

	\textbf{HSC}                                                          &                   \\
	Maharashtra State Board                                               & \textit{59.17\%}  \\
	\hline

	\textbf{SSC}                                                          &                   \\
	Maharashtra State Board                                               & \textit{93.07 \%} \\
	\hline
\end{tabularx}
\egroup
\vspace{2mm}

\end{document}

% LocalWords:  APACS eCommerce APIs TestNG mCommerce
